Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-22 paper.tex
added paper about parameter tuning
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Finally, ML techniques are already being used in the software verification area \cite{mlswverif,nguyen}. For instance, Hamel \cite{mlswverif} proposes to induce a theory, through ML, that fits a test set for a program, in such a way that it implement the respective test set. ML is already being employ in space state reduction, ML technique can be used also for invariant generation

@@

>>>>

Finally, ML techniques are already being used in the software verification area \cite{mlswverif,nguyen}. For instance, Hamel~\cite{mlswverif} proposes to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. ML is already being employed in space state reduction and to boost software verification by automatic tuning decision procedures~\cite{babic07}. ML technique can be used also for invariant generation.

@@

 %90
\bibitem{babic07}
Hutter F., Babic D., Hoos H. H., Hu A. J.              
\newblock {\em{Boosting Verification by Automatic Tuning of Decision Procedures.}}
\newblock {In 7th International Conference Formal Methods in Computer-Aided Design {(FMCAD)}, pp. 27--34, 2007.}
